One-stage point transect distance sampling using iterated integrated nested Laplace approximations

### 2024-10-28 paper.tex
add github to data availability statement

Code to reproduce the figures and results in this paper are available in a git repository and can be accessed at [git repo link].

@@

We are grateful to the many U.S. Fish and Wildlife Service staff and volunteers who helped collect the data through the Hawaiian Forest Bird survey. We thank Steve Buckland for helpful comments on an early draft.  Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. Government.

>>>>

Code to reproduce the figures and results in this paper are available in a git repository and can be accessed at \url{https://github.com/ASeatonSpatial/point-transects-paper/}.

@@

We are grateful to the many U.S. Fish and Wildlife Service staff and volunteers who helped collect the data through the \hawaii Forest Bird survey. We thank Steve Buckland for helpful comments on an early draft.  Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. Government.
